InformatiCup 2024 Ctrl-Alt-Defeat

### 2023-12-29 paper.tex
Update paper.tex

@@

The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI. In the training stage a detector tried to differentiate between human and AI text while a paraphraser trained to make the text more human.
The AI-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.

>>>>

The \textbf{ai-image-det-resnet18} model is a community made, fine tuned, resnet18 based, pretrained image detection model. For fine tuning the author kgmann on Hugging Face used the AI or Not dataset. ResNet-18 is a convolutional neural network that is 18 layers deep. It got pretrained by over a million images from the ImageNet database. \cite{he2015deep}

@@
